On the performance of the MAC model

### 2018-11-02 2018_nips_vigil/appendix.tex
Appendix, table with comparison of CoGenT results collected from different papers + explanation why and how we collected that data

The CoGenT task give a sense on how the model solve CLEVR question. Is the model learning combination of attributes or general representations?

@@

\section{Full MAC and S-MAC comparison}

@@

\begin{table}
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
		\cmidrule{7-8} 
		&                        &  &               &     &                                & CoGenT-A    &  96.22   \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   & 96.27  \\

@@

In this section we present comparison of MAC and S-MAC with selected state-of-the-art models as reported in~\cite{mascharka2018transparency} \tk{and? FiLM?}

\begin{table}[!h]
	\caption{Generalization capabilities of selected state-of-the-art models}
	\centering
	\begin{tabular}{cCcCcCc}
		\toprule
		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\

@@

		\bottomrule
	\end{tabular}
	\label{tab:generalization_comparison}
\end{table}

@@

The author inform that in the first step they trained their models on Condition A, and tested them on both Condition A and Condition B. 
Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both Conditions.
Sadly, it is not clear what sets exactly they used for fine-tuning (as Condition B contains only test set, thus lack training set) and testing on Condition A (as Condition A does not offer test set).
One possibility, as they are the authors of CLEVR and CoGenT datasets, is that they actually generated the missing sets, but didn't share them publicly.

@@

\cite{perez2017film})

We train our best model architecture on Condition A and report accuracies on Conditions A and B, before and
after fine-tuning on B, in Figure 9. Our results indicate FiLM
surpasses other visual reasoning models at learning general
concepts.

FiLM ValB accuracy reported on ValB without the 30K fine-tuning samples 
Accuracy before and after fine-tuning on 30K of ValB

Training A

@@

Performance comparison against the current state-of-the-
art model on the CoGenT dataset having trained only on Condition
A data (middle column) and after fine-tuning on a small amount
of data with novel attributes (right column).

Like pre-
vious  work  [14],  our  performance  is  worse  on  Condition
B than Condition A after training only using Condition A
data.  As Table 3 shows, our model achieves 98.8\% accu-
racy on Condition A, but only 75.4\% on Condition B. Fol-
lowing Johnson
et al
. [14], we then fine-tune our model us-
ing 3k images and 30k questions from the Condition B data.
Whereas other models see a significant drop in performance
on the Condition A data after fine-tuning, our model main-
tains high performance.  As Table 3 shows, our model can
effectively learn from a small amount of Condition B data.
We achieve 96.9\% accuracy on Condition A and 96.3\% ac-
curacy on Condition B after fine-tuning, far surpassing the
highest-reported 76.1\% Condition A and 92.7\% Condition
B accuracy.

@@

Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, the authors of~\cite{mascharka2018transparency} decided to split
the CoGenT validation sets and use part of then for training, and part for testing. 
We decided to follow that approach and ... \tk{Vincent, please proceed :)}

@@

\begin{figure}[]
	\centering
	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_shape.png}
	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}

@@

>>>>

@@

 \newpage
\section{Full MAC and S-MAC comparison}

@@

\begin{table}[!h]
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} &  \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		\multirow{15}{*}{MAC} & \multirow{10}{*}{CLEVR}  & \multirow{10}{*}{30:52}  & \multirow{10}{*}{96.70} & \multirow{4}{*}{--}   & \multirow{4}{*}{--}  & CLEVR    & 96.17          \\
		\cmidrule{7-8} 
		&                        &  &               &     &                                & CoGenT-A    &  96.22   \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   & 96.27  \\

@@

In this section we present comparison of our results on generalization capabilities with selected state-of-the-art models.
In particular, we focused on three papers reporting state-of-the-art accuracies, i.e. PG+EE~\cite{johnson2017inferring} FiLM~\cite{perez2017film} and TbD~\cite{mascharka2018transparency}.
Deeper analysis of the papers revealed that it is most probable that different authors used different sets for reporting the scores, which questions the correctness of the comparison.
We find that the problems result from the fact that answers for the test sets aren't provided along with those sets, thus researchers started to use subsets of the validation set for testing. 
The results of our research are presented in \tableref{tab:generalization_comparison}.
In the table we had to shorten the names of the datasets.
For example,  \textbf{A Test Full} means utilization of the whole \textbf{CoGenT Condition A Test set}, whereas  \textbf{B Valid 30k} indicates utilization of 30.000 samples from \textbf{CoGenT Condition B Validation set}.
Question marks indicate that the paper does not provide enough information and those are the sets we assumed were used.

\begin{table}[!h]
	\centering
	\begin{tabular}{cCcCcCc}
		\toprule
		Model & \multicolumn{2}{c}{Training} &    \multicolumn{2}{c}{Fine-tuning} &   \multicolumn{2}{c}{Test} \\		
		\cmidrule{2-3} \cmidrule{4-5}\cmidrule{6-7}
		(source)& CoGenT set & Acc [\%]  & CoGenT set & Acc [\%]  & CoGenT set~ & Acc [\%] \\

@@

		\bottomrule
	\end{tabular}
	\caption{Generalization capabilities of selected state-of-the-art models}
	\label{tab:generalization_comparison}
\end{table}

@@

The author inform that in the first step they trained their models on Condition A, and tested them on both Condition A and Condition B. 
Next, they fine-tuned these models on Condition B using 3K images and 30K questions, and again tested on both Conditions.
Sadly, it is not clear what sets exactly they used for fine-tuning (as Condition B lacks the training set).
One possibility, as they are the authors of CLEVR and CoGenT datasets, is that they actually generated the missing sets, but didn't share them publicly.
Besides, as they posses answers for both CoGenT Condition A and Condition B test sets, we are almost sure that they reported the accuracies on both Condition A and Condition B test sets.

@@

Feature-wise Linear Modulation (in short, FiLM)~\cite{perez2017film} is an optional enhancement of a neural network model.
The idea is to influence the behavior of existing layer(s) by introducing a feature-wise affine transformations that are conditioned on the input.
A model composed of FiLM enhanced CNN and GRU achieved state-of-the-art results on both CLEVR and CoGenT, showing few percent of improvements over the PG+EE model.

The problem with the presented comparison is that the authors used different sets for collecting the results, i.e. in the paper they clearly indicate that accuracies reported for Condition B after fine-tuning were calculated on CoGenT Condition B Validation set, excluding the 30k samples that were used for that fine-tuning.
This also suggests that they probably reported scores for CoGenT Condition A Validation set,
whereas, as it was mentioned previously, the original PG+EE paper probably relied on test sets in both cases.

@@

The TbD (Transparency by Design) network was introduced in~\cite{mascharka2018transparency}.
TbD is composed out of a set of visual reasoning primitives relying on attention transformations, allowing the model to perform reasoning by composes a series of attention mask.
The authors compare the accuracy of their model while tested on CLEVR  with several existing models, including mentioned PG + EE, CNN + GRU + FiLM and MAC, and once again indicate improvement.

They also compare accuracy on CoGenT, by comparison with PG+EE.
Despite the results show clear improvement, the section clearly lacks the most important information, i.e. which sets were used for training, fine-tuning and testing. 
The only provided information for sure is that they used 3k images and 30k questions from the CoGenT Condition B for fine-tuning of their model following~\cite{johnson2017inferring}, but do not mention from which set they took the samples.

@@

Due to the fact that test set targets for both CLEVR and CoGenT aren't publicly available, the authors of~\cite{perez2017film} decided to split
the CoGenT A Validation sets and use 30k samples for fine-tuning and the remaining part for testing.
When testing the model on CoGenT B, we used the whole Validation set.
In the experiments when we were using Validation B for fine-tuning, we did it analogically.
Besides that, as we were using Validation sets for testing, we also splitted the training set and used 90\% for training and remaining 10\% for validation during training.

@@

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{img/fail_mac_cogent_b_shape.png}
	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}
